Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-29 demystify.tex
updates

\paragraph{Core CS areas} The core CS areas that you should have knowledge in are:
\begin{itemize}
  \item Programming Foundation (e.g., programming in C/C++ or Java, OOP)
  \item Discrete Math (e.g., logic, set theory, proof techniques)
  \item Data Structures and Algorithms (e.g., linked lists, trees, sorting, searching)
  \item Computer OS or Systems (e.g., memory management, file systems, processes)
\end{itemize}

@@

Understandably students get excited about their upcoming PhD journey and want to buy new computer equipment and electronics to prepare. However, you should check with your adviser first.  Many profs. have funding to buy you computers and other equipments (e.g., software, books, keyboards, headphones, tablets, etc). Many CS programs also provide some budget or computer equipments to incoming PhD students (e.g., a laptop).

>>>>

\paragraph{Core CS areas} Common CS areas that you should have knowledge in are:
\begin{itemize}
  \item Programming Foundation (e.g., programming in C/C++ or Java, OOP)
  \item Discrete Math (e.g., logic, set theory, proof techniques)
  \item Data Structures and Algorithms (e.g., linked lists, trees, sorting, searching)
  \item Computer OS or Systems (e.g., memory management, file systems, processes)
\end{itemize}

@@

Understandably students get excited about their upcoming PhD journey and want to buy new computer equipment and electronics to prepare. However, you should check with your adviser first.  They might have funding to buy you computers and other equipments (e.g., software, books, keyboards, headphones, tablets, etc). Many CS programs also provide some budget or computer equipments to incoming PhD students (e.g., a laptop).
